%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------
\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Full Stack Developer}
{Elucidata} % Organization
{New Delhi, India} % Location
{July. 2017 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Successfully deployed 3 Angular application on }
\href{https://resources.elucidata.io/polly}{Polly Platform}
\item {Build Microservice architecture to deploy Jupyter Notebook, Knowledge Repo, Plotly Dash and Shiny Application on AWS by using kubernetes and docker}
\item {Worked directly with bio scientist(UCLA, Pfizer, Yale) to understand product requirements}
\item {Build RNA-Sequencing pipeline. It's also called whole transcriptome shotgun sequencing, uses next-generation sequencing to reveal the presence and quantity of RNA in a biological sample at a given moment. RNA-Seq is used to analyze the continuously changing cellular transcriptome.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Web Developer} % Job title
{Right Relevance} % Organization
{New Delhi, India} % Location
{Feb. 2017 - Mar. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked on the existing site, mainly dealing with the front end bugs fixing.}
\item {Learn new web technologies}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Frontend Developer} % Job title
{Grey Nexus} % Organization
{Bangalore, India} % Location
{Jan. 2017 - Feb. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked with the team of IIM’s and IIT’s alumni (Co-founders).}
\item {Worked on to build a social platform which is a network of educators, connecting and building a strong additional revenue system for them.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Web Developer, Project Head} % Job title
{Training and Placement Department, DTU} % Organization
{New Delhi, India} % Location
{Jun. 2016 - Jul. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Built a website for the department, currently in use by 3200 students.
}
\item {Developed a multilayered access levels for different login credentials (super admin, admin and a basic).
}
\item {Integrated with the google forms and linked sends collected data to the google spreadsheet for analysis.
}
\item {Managed a team of 5 for a successful multiplatform development of the product( web, app and spreadsheets).
}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Web Developer, Database Developer} % Job title
{Rahbar InfoTech Solution Pvt. Ltd} % Organization
{New Delhi, India} % Location
{Dec. 2015 - Jan. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed and developed an Online POS for a restaurant which can place order, generate bill and reports and can add new locations etc.
}
\item {Developed the Frontend and Backend using HTML5, JavaScript, CSS, Bootstrap, PHP and SQL.
}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Full Stack Developer} % Job title
{TravelExpoza} % Organization
{New Delhi, India} % Location
{Feb. 2016 - Mar. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed and developed a website (travel search engine) which give information about tour packages and suggest traveling ideas according to country, city, season etc.
}
\end{cvitems}
}

%------------------------------------------------

%------------------------------------------------

\end{cventries}
